Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-15 tuningpredictor.tex
Updates from ShareLaTeX

\begin{figure*}
\begin{center}
{\small\[\begin{array}{r|rrrrrrrrrrrrrrrrrr}\hline
          &      &      &       &   &       & 25th  &   & &  & 50th     &   &  &      & 75th  &   &   &     &\\
Precision & WHERE&	-30	&-10	&-2 &	0	&0	&0	&5&	6&	6	&7	&13&	40&	42&	59&	63&	72	&96\\

&CART&	-24&	-5	&-1	&1	&3	&3	&3	&6	&7	&7	&15&	16	&16&	29	&33&	58&	62\\

&RF &	-43&	-15&	-3	&-2	&-2&	-1	&0	&0	&0	&1	&1	&3	&5&	11&	19&	21	&50\\\hline 
f-measure &	WHERE&	-14&	-14	&-6&	-5	&-4	&-2&	0	&0	&2	&4	&5	&6	&7&	14&	28	&73	&87\\
	&CART	&-43	&-6	&-2&	-1&	1	&2	&5&	6&	6	&8	&12&	13&	16&	19&	19	&35&	57\\
	&RF	&-27	&-10	&-4	&-4&	-3	&-2	&-2	&-2&	0	&0	1&	2	&2	&2	&4	&5	&5
	\end{array} \]}
	\end{center}
\caption{Sorted performance deltas, {\em tuned - default} when tuning on precision in \fig{precisionbars}
and the F-measure in \fig{f-bars}.}
\end{figure*}
\subsection{Tuning Changes Learner Rankings}\label{sect:rank}

>>>>

\includegraphics[width=2.5in]{F.pdf}

\includegraphics[width=2.5in]{precision.pdf}

\subsection{Tuning Changes Learner Rankings}\label{sect:rank}
